### 2025-09-24 time-series-analysis.qmd
20250903 - updates to address updated data files
20250924 - syntax to load data object

The following code loads the Bayesian model object that was fit in @sec-fantasyPointsByAgeExperienceModelsBayesian.

```{r}
petersenlab::robust_load("https://osf.io/download/q6rjf/") #load(url("https://osf.io/download/q6rjf/")) # Bayesian model object
```

>>>>

We created the `player_stats_weekly.RData` and `player_stats_seasonal.RData` objects in @sec-calculatePlayerAge.
The following code loads the Bayesian model object that was fit in @sec-fantasyPointsByAgeExperienceModelsBayesian.

```{r}
#| eval: false

load(url("https://osf.io/download/q6rjf/")) # Bayesian model object
```

```{r}
#| include: false

petersenlab::robust_load("https://osf.io/download/q6rjf/") #load(url("https://osf.io/download/q6rjf/"))
```
